Supplemental Materials

### 2021-07-08 supplement/supplement-main.Rmd
added .rds outputs

if (!file.exists("../local/cv-res.rds")){
  source("../code/custom-structure-learning/fit-cog-models-bnlearn.R", chdir=TRUE)
}

cv_res <- readRDS("../local/cv-res.rds")

@@

# train_noise <- train %>%
#   mutate_all(~.x+rnorm(n(),0,.002))
if (!file.exists("../local/boot_res.rds")){
  cl = parallel::makeCluster(detectCores(logical=TRUE))

@@

  saveRDS(boot_res,"../local/boot_res.rds")
} else {
  boot_res <- readRDS("../local/boot_res.rds")
}

>>>>

if (!file.exists("../outputs/cv-res.rds")){
  source("../code/custom-structure-learning/fit-cog-models-bnlearn.R", chdir=TRUE)
} else {
  cv_res <- readRDS("../outputs/cv-res.rds")
}

@@

# train_noise <- train %>%
#   mutate_all(~.x+rnorm(n(),0,.002))
if (!file.exists("../outputs/boot-res.rds")){
  cl = parallel::makeCluster(detectCores(logical=TRUE))

@@

  saveRDS(boot_res,"../outputs/boot-res.rds")
} else {
  boot_res <- readRDS("../outputs/boot-res.rds")
}
